---
title: "Market Forecasting Assignment: Multiple Linear Regression"
author: "Teacher: Dr. Stefan Groesser, Dr.Christoph Imboden"
date: "Autor: Benedech Rodolpho, Buehler Pascal, Geeler Ken 04.12.2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = F)
knitr::opts_chunk$set(message  = F)
knitr::opts_chunk$set(fig.align = "center")
```

```{r, include=F,echo=T}
#library(kableExtra)
#mot=read.table("motorins.dat",header=T,sep = "")
#str(mot)
```

###  Short Theory Recap Multiple Linear Regression (MLR)
The model equation for MLR has the form  $y=X\Theta$ +$\epsilon$ ,with $y$ being the target vector, $X$ the explanatory Matrix,$\Theta$ the parameter vector and the residuals with the assumption that they are normally distributed  $\epsilon $~$ N(0,\sigma^{2})$. The estimation of $\Theta$ is done by solving the equation $\Theta=(X^{T}X)^{-1}X^{T}y$.

###  Dataset
The data is provided from Kaggle. Its data from 7 common fish species.

https://www.kaggle.com/aungpyaeap/fish-market


```{r, include=F,echo=T}
library(kableExtra)
fish_dat=read.csv("Fish.csv")
str(fish_dat)
```
